Abstract Binding Trees

### 2015-11-07 paper.tex
Add natural transformation to rename operators' parameters in interpretation

Next we have the interpretation of metavariable applications
\[%
  \SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash%
    \MApp{\MV{m}}{\vec{u}}{\vec{M}} : \tau}_P%
  \qquad(\Lookup{\Omega}{\MV{m}}{\MkValence{\vec{\sigma}}{\vec{\tau}}{\tau}})
\]
which proceeds by projecting the metavariable's interpretation from the
environment and intantiating it via substitution:
\[
  \begin{tikzcd}[ampersand replacement = \&, sep=huge]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
          \arrow[r, "\IMode{\Tuple{\pi_\MV{m}\,\pi_1, \phi\,\pi_2, \psi}}"]
    \& {\IMode{P_{\tau}^{\Yoneda{\vec{\sigma}\parallel\vec{\tau}}}\times S^{\{\vec{\sigma}\}} \times P^{[\vec{\tau}]}}}
          \arrow[r, "\IMode{\varsigma_{\vec{\sigma}\parallel\vec{\tau}}}"]
    \& \IMode{P_s}
  \end{tikzcd}
  \tag{metavar}
\]
where
\begin{align*}
  \ADefine{\phi}{
  \begin{tikzcd}[ampersand replacement = \&, sep=huge]
    {S^{\{\Upsilon\}}} \arrow[r, "\Tuple{\pi_u}_{u\in\vec{u}}"]
    \& {S^{\{\vec{\sigma}\}}}
  \end{tikzcd}
  }\\
  \ADefine{\psi}{
   \begin{tikzcd}[ampersand replacement = \&, sep=28ex]
     {\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}
        \arrow[r, "\Tuple{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash M:\tau}_P}_{(M,\tau)\in \vec{M}\otimes\vec{\tau}}"]
     \& {P^{[\vec{\tau}]}}
   \end{tikzcd}
  }
\end{align*}

>>>>

Next we have the interpretation of metavariable applications
\[%
  \SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash%
    \MApp{\MV{m}}{\vec{u}}{\vec{M}} : \tau}_P%
  \qquad(\Lookup{\Omega}{\MV{m}}{\MkValence{\vec{\sigma}}{\vec{\tau}}{\tau}})
\]
which proceeds by projecting the metavariable's interpretation from the
environment and intantiating it via substitution:
\[
  \begin{tikzcd}[ampersand replacement = \&, sep=huge]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
          \arrow[r, "\IMode{\Tuple{\pi_\MV{m}\,\pi_1, \phi\,\pi_2, \psi}}"]
    \& {\IMode{P_{\tau}^{\Yoneda{\vec{\sigma}\parallel\vec{\tau}}}\times S^{\{\vec{\sigma}\}} \times P^{[\vec{\tau}]}}}
          \arrow[r, "\IMode{\varsigma_{\vec{\sigma}\parallel\vec{\tau}}}"]
    \& \IMode{P_s}
  \end{tikzcd}
  \tag{metavar}
\]
where
\begin{align*}
  \ADefine{\phi}{
  \begin{tikzcd}[ampersand replacement = \&, sep=huge]
    {S^{\{\Upsilon\}}} \arrow[r, "\Tuple{\pi_u}_{u\in\vec{u}}"]
    \& {S^{\{\vec{\sigma}\}}}
  \end{tikzcd}
  }\\
  \ADefine{\psi}{
   \begin{tikzcd}[ampersand replacement = \&, sep=28ex]
     {\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}
     \arrow[r, "\Tuple{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash M:\tau}_P}_{(M,\tau)\in (\vec{M},\vec{\tau})}"]
     \& {P^{[\vec{\tau}]}}
   \end{tikzcd}
  }
\end{align*}

The interpretation of operator applications is most complicated. Recall that,
unlike in standard treatments of algebraic theories, our operators are indexed
by symbol collections; therefore, operators must pass through suitable
renamings in order to be used in the interpretation. Let us begin by
constructing for each operator $\IsOperator{\Upsilon}{\vartheta}{a}$ the
natural transformation
$\Of{\SemBrackets{\vartheta}_P}{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
\to\Operators_{a}}$, which shall rename the parameters of the operator using
the environment.

\[
  \Define{
    \SemBrackets{\vartheta}_P
  }{
   \begin{tikzcd}[ampersand replacement = \&, sep=large]
     {\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P} \arrow[r, "\pi_2"]
     \& {S^{\{\Upsilon\}}} \arrow[r, "\FLift{\pi_{(-)}}{}"]
     \& {\Operators_a}
   \end{tikzcd}
 }
\]
